### 2023-08-29 proofs/tex/constraint-merge-lemmas.tex
WIP: update typing lemmas

\begin{lemma} [Soundness of Constraint Entry Merge]
\label{lemma:entry-merge-soundness}
For a fixed context $[[Γ]]$,
suppose that  $[[Γ ⊢ scE1]]$ and $[[Γ ⊢ scE2]]$. 
If $[[Γ ⊢ scE1 & scE2 = scE]]$ is defined then
\begin{enumerate}
    \item $[[Γ ⊢ scE]]$
    \item For any $[[Γ ⊢ iP]]$, $[[Γ ⊢ iP : scE]]$ implies $[[Γ ⊢ iP : scE1]]$ and $[[Γ ⊢ iP : scE2]]$ 
\end{enumerate}
\end{lemma}
\begin{proof}
    Let us consider the rule forming $[[Γ ⊢ scE1 & scE2 = scE]]$.
    \begin{caseof}
        \item \ruleref{\ottdruleSCMEPEqEqLabel}, i.e. 
        $[[Γ ⊢ scE1 & scE2 = scE]]$
        has form $[[Γ ⊢ (pua :≈ iQ) & (pua :≈ iQ') = (pua :≈ iQ)]]$
        and $[[nf(iQ) = nf(iQ')]]$. The latter implies $[[Γ ⊢ iQ ≈ iQ']]$ by
        \cref{lemma:subt-equiv-algorithmization}.
        Then
        \begin{enumerate}
            \item $[[Γ ⊢ scE]]$, i.e. $[[Γ ⊢ pua :≈ iQ]]$ holds by assumption;
            \item by inversion, $[[Γ ⊢ iP : (pua :≈ iQ)]]$ means $[[Θ ⊢ iP ≈ iQ]]$,
            and by transitivity of equivalence (\cref{corollary:equivalence-transitivity}), 
            $[[Θ ⊢ iP ≈ iQ']]$. Thus, $[[Γ ⊢ iP : scE1]]$ and $[[Γ ⊢ iP : scE2]]$ hold
            by \ruleref{\ottdruleSATSCEPEqLabel}.
        \end{enumerate}
        \item \ruleref{\ottdruleSCMENEqEqLabel} the negative case is proved in exactly the same way as the positive one.
        \item \ruleref{\ottdruleSCMESupSupLabel} 
        Then $[[scE1]]$ is $[[pua :≥ iQ1]]$, $[[scE2]]$ is $[[pua :≥ iQ2]]$,
        and $[[scE1 & scE2]] = [[scE]]$ is $[[pua :≥ iQ]]$ where $[[iQ]]$ is the least upper bound of $[[iQ1]]$ and $[[iQ2]]$.
        Then by \cref{lemma:lub-soundness},
        \begin{itemize}
            \item $[[Γ ⊢ iQ]]$,
            \item $[[Γ ⊢ iQ ≥ iQ1]]$,
            \item $[[Γ ⊢ iQ ≥ iQ2]]$.
        \end{itemize}

@@

\begin{lemma} [Soundness of Constraint Merge] \label{lemma:merge-soundness}
    Suppose that $[[Θ ⊢ SC1]]$ and $[[Θ ⊢ SC2]]$ 
    and $[[Θ ⊢ SC1 & SC2 = SC]]$ is defined.
    Then 
    \begin{enumerate}
        \item $[[Θ ⊢ SC]]$,
        \item for any substitution $[[Θ ⊢ uσ]]$, $[[Θ ⊢ uσ : SC]]$ implies $[[Θ ⊢ uσ : SC1]]$ and $[[Θ ⊢ uσ : SC2]]$.
    \end{enumerate}
\end{lemma}
\begin{proof}
    By definition, $[[SC1 & SC2]] = [[SC]]$ consists of three parts:
    entries of $[[SC1]]$ that do not have matching entries of $[[SC]]$,
    entries of $[[SC2]]$ that do not have matching entries of $[[SC1]]$,
    and the merge of matching entries.

    Let us show $[[Θ ⊢ SC]]$.
    First, let us assume that an entry $[[scE]] \in [[SC]]$ belongs to the first group, 
    i.e. $[[scE]] \in [[SC1]]$.  Let us denote the variable $[[scE]]$ as $[[α̂±]]$. 
    Then $[[Θ(α̂±) ⊢ scE]]$ holds since $[[Θ ⊢ SC1]] \ni [[scE]]$.
    Analogously, if $[[scE]]$ belongs to the second group, then $[[Θ(α̂±) ⊢ scE]]$ holds since $[[Θ ⊢ SC2]] \ni [[scE]]$.
    Finally, if $[[scE]]$ belongs to the third group, then $[[scE]]$ is a merge of two entries $[[Θ(α̂±) ⊢ scE1]]$ 
    and $[[Θ(α̂±) ⊢ scE2]]$.  Then $[[Θ(α̂±) ⊢ scE]]$ holds by \cref{lemma:entry-merge-soundness}.

    Let us show the second property.
    We take an arbitrary $[[uσ]]$ such that $[[Θ ⊢ uσ]]$ and $[[Θ ⊢ uσ : SC]]$.
    To prove $[[Θ ⊢ uσ : SC1]]$, we need to show that for any $[[scE1]] \in [[SC1]]$, restricting $[[α̂±]]$,
    $[[Θ(α̂±) ⊢ [uσ]α̂± : scE1]]$ holds.

    Let us assume that $[[α̂±]] \notin [[dom(SC2)]]$. It means that $[[SC]] \ni [[scE1]]$, 
    and then since $[[Θ ⊢ uσ : SC]]$, $[[Θ(α̂±) ⊢ [uσ]α̂± : scE1]]$.

    Otherwise, $[[SC2]]$ contains an entry $[[scE2]]$ restricting $[[α̂±]]$,
    and $[[SC]] \ni [[scE]]$ where $[[Θ(α̂±) ⊢ scE1 & scE2 = scE]]$.
    Then since $[[Θ ⊢ uσ : SC]]$, $[[Θ(α̂±) ⊢ [uσ]α̂± : scE]]$,
    and by \cref{lemma:entry-merge-soundness}, $[[Θ(α̂±) ⊢ [uσ]α̂± : scE1]]$.

    The proof of $[[Θ ⊢ uσ : SC2]]$ is symmetric.
\end{proof}

@@

\begin{lemma} [Completeness of Constraint Merge] 
    \label{lemma:merge-completeness}
    Suppose that $[[Θ ⊢ SC1]]$ and $[[Θ ⊢ SC2]]$.
    Then for any substitution $[[Θ ⊢ uσ]]$ such that $[[Θ ⊢ uσ : SC1]]$ and $[[Θ ⊢ uσ : SC2]]$, 
    $[[Θ ⊢ SC1 & SC2 = SC]]$ is defined.
\end{lemma}
\begin{proof}
    By  definition, $[[SC1 & SC2]]$ is a union of
    \begin{enumerate}
        \item entries of $[[SC1]]$, which do not have matching entries in $[[SC2]]$,
        \item entries of $[[SC2]]$, which do not have matching entries in $[[SC1]]$, and 
        \item the merge of matching entries.
    \end{enumerate}

    This way, to show that $[[Θ ⊢ SC1 & SC2 = SC]]$ is defined, we need to demonstrate that each of these components is defined.

    It is clear that the first two components of this union exist. 
    Let us show that the third component exists.  
    Let us take two entries $[[scE1]] \in [[SC1]]$ and $[[scE2]] \in [[SC2]]$ restricting the same variable $[[α̂±]]$.  $[[Θ ⊢ uσ : SC1]]$ means that $[[Θ(α̂±) ⊢ [uσ]α̂± : scE1]]$ and $[[Θ ⊢ uσ : SC2]]$ means $[[Θ(α̂±) ⊢ [uσ]α̂± : scE2]]$.
    Then by \cref{lemma:entry-merge-completeness}, $[[Θ(α̂±) ⊢ scE1 & scE2 = scE]]$ is defined and $[[Θ(α̂±) ⊢ [uσ]α̂± : scE]]$.
\end{proof}

\begin{lemma}[Substitution existence]
    \label{lemma:substitution-existence}
    If $[[Θ ⊢ SC]]$ then there exists $[[Θ ⊢ uσ]]$ such that $[[Θ ⊢ uσ : SC]]$.
\end{lemma}
\begin{proof}

>>>>

\begin{lemma} [Soundness of Constraint Entry Merge]
    \label{lemma:entry-merge-soundness}
    For a fixed context $[[Γ]]$,
    suppose that  $[[Γ ⊢ scE1]]$ and $[[Γ ⊢ scE2]]$. 
    If $[[Γ ⊢ scE1 & scE2 = scE]]$ is defined then
    \begin{enumerate}
        \item $[[Γ ⊢ scE]]$
        \item For any $[[Γ ⊢ iP]]$, $[[Γ ⊢ iP : scE]]$ implies $[[Γ ⊢ iP : scE1]]$ and $[[Γ ⊢ iP : scE2]]$ 
    \end{enumerate}
\end{lemma}
\begin{proof}
    Let us consider the rule forming $[[Γ ⊢ scE1 & scE2 = scE]]$.
    \begin{caseof}
        \item \ruleref{\ottdruleSCMEPEqEqLabel}, i.e. 
            $[[Γ ⊢ scE1 & scE2 = scE]]$
            has form $[[Γ ⊢ (pua :≈ iQ) & (pua :≈ iQ') = (pua :≈ iQ)]]$
            and $[[nf(iQ) = nf(iQ')]]$. The latter implies $[[Γ ⊢ iQ ≈ iQ']]$ by
            \cref{lemma:subt-equiv-algorithmization}.
            Then
            \begin{enumerate}
                \item $[[Γ ⊢ scE]]$, i.e. $[[Γ ⊢ pua :≈ iQ]]$ holds by assumption;
                \item by inversion, $[[Γ ⊢ iP : (pua :≈ iQ)]]$ means $[[Γ ⊢ iP ≈ iQ]]$,
                and by transitivity of equivalence (\cref{corollary:equivalence-transitivity}), 
                $[[Γ ⊢ iP ≈ iQ']]$. Thus, $[[Γ ⊢ iP : scE1]]$ and $[[Γ ⊢ iP : scE2]]$ hold
                by \ruleref{\ottdruleSATSCEPEqLabel}.
            \end{enumerate}
        \item \ruleref{\ottdruleSCMENEqEqLabel} the negative case is proved in exactly the same way as the positive one.
        \item \ruleref{\ottdruleSCMESupSupLabel} 
            Then $[[scE1]]$ is $[[pua :≥ iQ1]]$, $[[scE2]]$ is $[[pua :≥ iQ2]]$,
            and $[[scE1 & scE2]] = [[scE]]$ is $[[pua :≥ iQ]]$ where $[[iQ]]$ is the least upper bound of $[[iQ1]]$ and $[[iQ2]]$.
            Then by \cref{lemma:lub-soundness},
            \begin{itemize}
                \item $[[Γ ⊢ iQ]]$,
                \item $[[Γ ⊢ iQ ≥ iQ1]]$,
                \item $[[Γ ⊢ iQ ≥ iQ2]]$.
            \end{itemize}

@@

\begin{lemma} [Soundness of Constraint Merge] \label{lemma:merge-soundness}
    Suppose that $[[Θ ⊢ SC1 : Ξ1]]$ and $[[Θ ⊢ SC2 : Ξ2]]$ 
    and $[[Θ ⊢ SC1 & SC2 = SC]]$ is defined.
    Then 
    \begin{enumerate}
        \item $[[Θ ⊢ SC : Ξ1 ∪ Ξ2]]$,
        \item for any substitution $[[Θ ⊢ uσ : Ξ1 ∪ Ξ2]]$, 
            $[[ Θ ⊢ uσ : SC ]]$
            implies $[[ Θ ⊢ uσ : SC1 ]]$ and $[[ Θ ⊢ uσ : SC2 ]]$.
    \end{enumerate}
\end{lemma}
\begin{proof}
    By definition, $[[Θ ⊢ SC1 & SC2 = SC]]$ consists of three parts:
    entries of $[[SC1]]$ that do not have matching entries of $[[SC2]]$,
    entries of $[[SC2]]$ that do not have matching entries of $[[SC1]]$,
    and the merge of matching entries.

    Notice that $[[α̂± ∊ Ξ1 \ Ξ2]]$
    if and only if there is an entry $[[scE]]$ in $[[SC1]]$ 
    restricting $[[α̂±]]$, but there is no such entry in $[[SC2]]$.
    Therefore, for any $[[α̂± ∊ Ξ1 \ Ξ2]]$,
    there is an entry $[[scE]]$ in $[[SC]]$ restricting $[[α̂±]]$.
    Notice that $[[Θ(α̂±) ⊢ scE]]$ holds since $[[Θ ⊢ SC1 : Ξ1]]$.

    Analogously, for any $[[β̂± ∊ Ξ2 \ Ξ1]]$,
    there is an entry $[[scE]]$ in $[[SC]]$ restricting $[[β̂±]]$.
    Notice that  $[[Θ(β̂±) ⊢ scE]]$ holds since $[[Θ ⊢ SC2 : Ξ2]]$.

    Finally, for any $[[γ̂± ∊ Ξ1 ∩ Ξ2]]$,
    there is an entry $[[scE1]]$ in $[[SC1]]$ restricting $[[γ̂±]]$
    and an entry $[[scE2]]$ in $[[SC2]]$ restricting $[[γ̂±]]$.
    Since $[[Θ ⊢ SC1 & SC2 = SC]]$ is defined,
    $[[Θ(γ̂±) ⊢ scE1 & scE2 = scE]]$ restricting $[[γ̂±]]$ is
    defined and belongs to $[[SC]]$,
    moreover, $[[Θ(γ̂±) ⊢ scE]]$ by \cref{lemma:entry-merge-soundness}.
    This way, $[[Θ ⊢ SC : Ξ1 ∪ Ξ2]]$.

    Let us show the second property.
    We take an arbitrary $[[uσ]]$ such that $[[Θ ⊢ uσ : Ξ1 ∪ Ξ2]]$ 
    and $[[ Θ ⊢ uσ : SC ]]$.
    To prove $[[ Θ ⊢ uσ : SC1 ]]$, 
    we need to show that for any $[[scE1]] \in [[SC1]]$, 
    restricting $[[α̂±]]$, $[[Θ(α̂±) ⊢ [uσ]α̂± : scE1]]$ holds.

    Let us assume that $[[α̂±]] \notin [[dom(SC2)]]$. It means that $[[SC]] \ni [[scE1]]$, 
    and then since $[[ Θ ⊢ uσ : SC ]]$, $[[Θ(α̂±) ⊢ [uσ]α̂± : scE1]]$.

    Otherwise, $[[SC2]]$ contains an entry $[[scE2]]$ restricting $[[α̂±]]$,
    and $[[SC]] \ni [[scE]]$ where $[[Θ(α̂±) ⊢ scE1 & scE2 = scE]]$.
    Then since $[[ Θ ⊢ uσ : SC ]]$, $[[Θ(α̂±) ⊢ [uσ]α̂± : scE]]$,
    and by \cref{lemma:entry-merge-soundness}, $[[Θ(α̂±) ⊢ [uσ]α̂± : scE1]]$.

    The proof of $[[ Θ ⊢ uσ : SC2 ]]$ is symmetric.
\end{proof}

@@

\begin{lemma} [Completeness of Constraint Merge] 
    \label{lemma:merge-completeness}
    Suppose that $[[Θ ⊢ SC1 : Ξ1]]$ and $[[Θ ⊢ SC2 : Ξ2]]$.
    If there exists a substitution $[[Θ ⊢ uσ : Ξ1 ∪ Ξ2]]$ such that 
    $[[ Θ ⊢ uσ : SC1 ]]$ and $[[ Θ ⊢ uσ : SC2 ]]$
    then $[[Θ ⊢ SC1 & SC2 = SC]]$ is defined,
    and $[[ Θ ⊢ uσ : SC ]]$.
\end{lemma}
\begin{proof}
    By  definition, $[[SC1 & SC2]]$ is a union of
    \begin{enumerate}
        \item entries of $[[SC1]]$, which do not have matching entries in $[[SC2]]$,
        \item entries of $[[SC2]]$, which do not have matching entries in $[[SC1]]$, and 
        \item the merge of matching entries.
    \end{enumerate}

    This way, to show that $[[Θ ⊢ SC1 & SC2 = SC]]$ is defined, we need to demonstrate that 
    each of these components is defined and satisfies 
    the required property 
    (that the result of $[[uσ]]$ satisfies the corresponding constraint entry).

    It is clear that the first two components of this union exist. 
    Moreover, if $[[scE]]$ is an entry of $[[SCi]]$
    restricting $[[α̂± ∉ dom(SC2)]]$,
    then $[[ Θ ⊢ uσ : SCi ]]$ implies $[[ Θ(α̂±) ⊢ [uσ]α̂± : scE]]$,

    Let us show that the third component exists.  
    Let us take two entries $[[scE1]] \in [[SC1]]$ and $[[scE2]] \in [[SC2]]$ restricting the same variable $[[α̂±]]$.  $[[ Θ   ⊢ uσ : SC1 ]]$ means that $[[Θ(α̂±) ⊢ [uσ]α̂± : scE1]]$ and $[[ Θ   ⊢ uσ : SC2 ]]$ means $[[Θ(α̂±) ⊢ [uσ]α̂± : scE2]]$.
    Then by \cref{lemma:entry-merge-completeness}, $[[Θ(α̂±) ⊢ scE1 & scE2 = scE]]$ is defined and $[[Θ(α̂±) ⊢ [uσ]α̂± : scE]]$.

### 2023-08-29 proofs/tex/singularity-lemmas.tex
WIP: update typing lemmas

\begin{lemma}[Soundness of Singularity]
    \label{lemma:singularity-soundness}
    Suppose $[[Θ ⊢ SC]]$, and $[[SC singular with uσ]]$. 
    Then $[[Θ ⊢ uσ : SC]]$ and for any 
    $[[uσ']]$ such that $[[Θ ⊢ uσ' : SC]]$,
    $[[Θ ⊢ uσ' ≈ uσ : dom(SC)]]$.
\end{lemma}
\begin{proof}
    Suppose that $[[Θ ⊢ uσ' : SC]]$.
    It means that for every $[[scE]] \in [[SC]]$ restricting $[[α̂±]]$,
    $[[Θ(α̂±) ⊢ [uσ']α̂± : scE]]$ holds.
    $[[SC singular with uσ]]$ means $[[scE singular with [uσ]α̂± ]]$,
    and hence, by \cref{lemma:entry-singularity-completeness},
    $[[ Θ(α̂±) ⊢ [uσ']α̂± ≈ [uσ]α̂±  ]]$ holds.

@@

\begin{lemma}[Completeness of Singularity]
\end{lemma}

\begin{lemma}[Completeness of Singularity]
    \label{lemma:singularity-completeness}
    Suppose there exists $[[Θ ⊢ uσ1]]$ such that
    for any $[[Θ ⊢ uσ]]$, $[[Θ ⊢ uσ : SC]]$ implies $[[Θ ⊢ uσ ≈ uσ1 : varset]]$.
    Then 
    \begin{itemize}
        \item $[[SC|varset singular with uσ0]]$ for some $[[uσ0]]$, and
        \item $[[varset ⊆ dom(SC)]]$.
    \end{itemize} 
\end{lemma}
\begin{proof}
\end{proof}

>>>>

\begin{lemma}[Soundness of Singularity]
    \label{lemma:singularity-soundness}
    Suppose $[[Θ ⊢ SC : Ξ]]$, and $[[SC singular with uσ]]$. 
    Then $[[ Θ ⊢ uσ : Ξ ]]$,
     $[[ Θ ⊢ uσ : SC ]]$ and for any 
    $[[uσ']]$ such that $[[Θ ⊢ uσ : SC]]$,
    $[[Θ ⊢ uσ' ≈ uσ : Ξ]]$.
\end{lemma}
\begin{proof}
    Suppose that $(Θ  ⊢ SC) ⊢ uσ'$.
    It means that for every $[[scE]] \in [[SC]]$ restricting $[[α̂±]]$,
    $[[Θ(α̂±) ⊢ [uσ']α̂± : scE]]$ holds.
    $[[SC singular with uσ]]$ means $[[scE singular with [uσ]α̂± ]]$,
    and hence, by \cref{lemma:entry-singularity-completeness},
    $[[ Θ(α̂±) ⊢ [uσ']α̂± ≈ [uσ]α̂±  ]]$ holds.

@@

\begin{lemma}[Completeness of Singularity]
    \label{lemma:singularity-completeness}
    For a given $[[Θ ⊢ SC : Ξ]]$,
    suppose that all the substitutions satisfying $[[SC]]$ are equivalent
    on $[[Ξ']] \supseteq [[Ξ]]$.
    In other words, suppose that there exists $[[Θ ⊢ uσ1 : Ξ']]$ such that
    for any $[[Θ ⊢ uσ : Ξ']]$, $[[Θ ⊢ uσ : SC]]$ implies 
    $[[Θ ⊢ uσ ≈ uσ1 : Ξ']]$.
    Then 
    \begin{itemize}
        \item $[[SC singular with uσ0]]$ for some $[[uσ0]]$ and
        \item $[[Ξ']] = [[Ξ]]$.
    \end{itemize} 
\end{lemma}
\begin{proof}
    First, let us suppose that $[[varset ⊆ dom(SC)]]$ does not hold.
    It means that there exists $[[ α̂±[Γ] ∊ Θ]]$ and $[[α̂± ∉ dom(SC)]]$

    By \cref{lemma:constraint-sat}, let us take an arbitrary 
    $[[uσ']]$ satisfying $[[SC]]$ (that is $[[ Θ   ⊢ uσ' : SC ]]$).
    Let us extend $[[uσ']]$ to $[[uσ'']]$ so that $[[Θ ⊢ uσ'']]$.

    Although $[[uσ']]$ might not be defined on

    such that for any $[[Θ ⊢ uσ]]$, $[[ Θ   ⊢ uσ : SC ]]$ implies 
    $[[ Γ ⊢ [uσ]α̂± ≈ [uσ1]α̂± ]]$.
    Let us take

    for any $[[Θ ⊢ uσ]]$, $[[ Θ   ⊢ uσ : SC ]]$ implies $[[Θ|varset ⊢ uσ ≈ uσ1]]$.

        \item [$-$] Suppose that there exists $[[iN]]$ well-formed in $[[Γ]]$ 
            such that for any $[[iN']]$ well-formed in $[[Γ]]$,
            $[[Γ ⊢ iN' : scE]]$ implies $[[Γ ⊢ iN' ≈ iN]]$. 
            Then $[[scE singular with nf(iN)]]$.
        \item [$+$] Suppose that there exists $[[iP]]$ well-formed in $[[Γ]]$ 
            such that for any $[[iP']]$ well-formed in $[[Γ]]$,
            $[[Γ ⊢ iP' : scE]]$ implies $[[Γ ⊢ iP' ≈ iP]]$. 
            Then $[[scE singular with nf(iP)]]$ .

### 2023-08-29 proofs/tex/subst-lemmas.tex
WIP: update typing lemmas

>>>>

\begin{lemma}[Algorithmic Substitution strengthening]
  \label{lemma:subst-restr-uv}
  Restricting the substitution to the free algorithmic 
  variables of the
  substitution subject does not affect the result.
  Suppose that $[[uσ]]$ is an algorithmic substitution,
  $[[uP]]$ and $[[uN]]$ are algorithmic types. Then
 \begin{itemize}
    \item[$+$] $[[ [uσ]uP ]] = [[ [uσ|uv uP]uP ]]$,
    \item[$-$] $[[ [uσ]uN ]] = [[ [uσ|uv iN]uN ]]$
  \end{itemize}
\end{lemma}
\begin{proof}
  The proof is analogous to the proof of \cref{lemma:subst-restr-fv}.
\end{proof}

### 2023-08-29 proofs/tex/unif-constraint-merge-lemmas.tex
WIP: update typing lemmas

\begin{corollary}
    \label{corollary:unif-merge-soundness}
    Suppose that $[[Θ ⊢ UC1]]$ and $[[Θ ⊢ UC2]]$ 
    are normalized unification constraints.
    If $[[Θ ⊢ UC1 & UC2 = UC]]$ is defined then
    \begin{enumerate}
        \item $[[Θ ⊢ UC]]$ is normalized unification constraint,
        \item for any substitution $[[Θ ⊢ uσ]]$, $[[Θ ⊢ uσ : lift UC]]$ implies 
        $[[Θ ⊢ uσ : lift UC1]]$ and $[[Θ ⊢ uσ : lift UC2]]$.
    \end{enumerate}
\end{corollary}
\begin{proof}
    It is clear that since $[[UC = UC1 ∪ UC2]]$ (by \cref{lemma:unif-merge-soundness}),
    and being normalized means that all entries are normalized,
    $[[UC]]$ is a normalized unification constraint.
    Analogously, $[[Θ ⊢ UC]] = [[UC1 ∪ UC2]]$ holds immediately, 
    since $[[Θ ⊢ UC1]]$ and $[[Θ ⊢ UC2]]$.

    Let us take an arbitrary substitution $[[Θ ⊢ uσ]]$ and assume that 
    $[[Θ ⊢ uσ : lift UC]]$.
    Then $[[Θ ⊢ uσ : lift UCi]]$ holds by definition:
    If $[[ucE]] \in [[lift UCi]] \subseteq [[lift UC1 ∪ lift UC2]] = [[lift UC]]$.
    So $[[Θ(α̂±) ⊢ [uσ]α̂± : ucE]]$ holds.
\end{proof}

@@

\begin{lemma} [Completeness of Unification Constraint Merge] 
    \label{lemma:unif-merge-completeness}
    Suppose that $[[Θ ⊢ UC1]]$ and $[[Θ ⊢ UC2]]$.
    Then for any substitution $[[Θ ⊢ uσ]]$ such that $[[Θ ⊢ uσ : lift UC1]]$ and $[[Θ ⊢ uσ : lift UC2]]$, 
    \begin{enumerate}
        \item $[[Θ ⊢ UC1 & UC2 = UC]]$ is defined and
        \item $[[Θ ⊢ uσ : UC]]$.
    \end{enumerate}
\end{lemma}
\begin{proof}
    The proof repeats the proof of \cref{lemma:merge-completeness} but 
    uses \cref{lemma:unif-entry-merge-completeness} instead of \cref{lemma:entry-merge-completeness}.
\end{proof}

>>>>

\begin{corollary}
    \label{corollary:unif-merge-soundness}
    Suppose that $[[Θ ⊢ UC1]]$ and $[[Θ ⊢ UC2]]$ 
    are normalized unification constraints.
    If $[[Θ ⊢ UC1 & UC2 = UC]]$ is defined then
    \begin{enumerate}
        \item $[[Θ ⊢ UC]]$ is normalized unification constraint,
        \item for any substitution $[[Θ ⊢ uσ]]$, $[[ Θ   ⊢ uσ : lift UC ]]$ implies 
        $[[ Θ   ⊢ uσ : lift UC1 ]]$ and $[[ Θ   ⊢ uσ : lift UC2 ]]$.
    \end{enumerate}
\end{corollary}
\begin{proof}
    It is clear that since $[[UC = UC1 ∪ UC2]]$ (by \cref{lemma:unif-merge-soundness}),
    and being normalized means that all entries are normalized,
    $[[UC]]$ is a normalized unification constraint.
    Analogously, $[[Θ ⊢ UC]] = [[UC1 ∪ UC2]]$ holds immediately, 
    since $[[Θ ⊢ UC1]]$ and $[[Θ ⊢ UC2]]$.

    Let us take an arbitrary substitution $[[Θ ⊢ uσ]]$ and assume that 
    $[[ Θ   ⊢ uσ : lift UC ]]$.
    Then $[[ Θ   ⊢ uσ : lift UCi ]]$ holds by definition:
    If $[[ucE]] \in [[lift UCi]] \subseteq [[lift UC1 ∪ lift UC2]] = [[lift UC]]$.
    So $[[Θ(α̂±) ⊢ [uσ]α̂± : ucE]]$ holds.
\end{proof}

@@

\begin{lemma} [Completeness of Unification Constraint Merge] 
    \label{lemma:unif-merge-completeness}
    Suppose that $[[Θ ⊢ UC1]]$ and $[[Θ ⊢ UC2]]$.
    Then for any substitution $[[Θ ⊢ uσ]]$ such that $[[ Θ   ⊢ uσ : lift UC1 ]]$ and $[[ Θ   ⊢ uσ : lift UC2 ]]$, 
    \begin{enumerate}
        \item $[[Θ ⊢ UC1 & UC2 = UC]]$ is defined and
        \item $[[ Θ   ⊢ uσ : UC ]]$.
    \end{enumerate}
\end{lemma}
\begin{proof}
    The proof repeats the proof of \cref{lemma:merge-completeness} but 
    uses \cref{lemma:unif-entry-merge-completeness} instead of \cref{lemma:entry-merge-completeness}.
\end{proof}
